Supplement 2

### 2020-09-10 paper/supplement-2.Rmd
update data munging from work meeting

---
title: "Supplement 2"
output: 
  bookdown::html_document2
  # bookdown::pdf_document2
bibliography: "supp-2.bib"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE)
```

```{r libraries, message = FALSE}
library(tidyverse)
library(kableExtra)
library(knitr)
library(conflicted)
library(gt)
library(PRISMAstatement)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")
```

@@

Football related articles published in 2019 were studied. Three major
sports medicine databases were searched on May 20, 2020, using key terms and limits. 
The databases were: SPORTDiscus, Embase and Cinahl. A
list of the search terms and complete search statements are provided in
Table \@ref(tab:search-table).

```{r search-table}
search_table <- tibble(
  Sportdiscus = c("exercise science OR sports science OR physiology OR biomechanics OR nutrition OR training OR testing OR sports medicine OR performance analysis OR performance OR sport psychology OR coaching",
    "football OR soccer OR indoor soccer OR futsal OR rugby league OR rugby union OR gaelic football OR australian rules football OR AFL OR american football OR gridiron football OR touch football",
    "Published Date: 20190101-20191231; English Abstract Available; Peer Reviewed",
    "Articles: 1,372",
    "https://gateway.library.qut.edu.au/login?url=https://search.ebscohost.com/login.aspx?direct=true&db=sph&bquery=(((football)+OR+(soccer)+OR+(indoor+soccer)+OR+(futsal)+OR+(rugby+league)+OR+(rugby+union)+OR+(gaelic+football)+OR+(australian+rules+football)+OR+(AFL)+OR+(american+football)+OR+(gridiron+football)+OR+(touch+football)))+AND+(((exercise+science)+OR+(sports+science)+OR+(physiology)+OR+(biomechanics)+OR+(nutrition)+OR+(training)+OR+(testing)+OR+(sports+medicine)+OR+(performance+analysis)+OR+(performance)+OR+(sport+psychology)+OR+(coaching)))&cli0=DT1&clv0=201901-201912&cli1=AA1&clv1=Y&cli2=RV&clv2=Y&authtype=sso&custid=qut&type=1&searchMode=Standard&site=ehost-live&scope=site"),
  Embase = c("(exercise AND science OR (sports AND science) OR physiology OR biomechanics OR nutrition OR training OR testing OR (sports AND medicine) OR 'performance analysis' OR (('performance'/exp OR performance) AND ('analysis'/exp OR analysis)) OR 'performance'/exp OR performance OR 'sport psychology'/exp OR 'sport psychology' OR (('sport'/exp OR sport) AND ('psychology'/exp OR psychology)) OR 'coaching'/exp OR coaching) AND [2019-2019]/py",
              "(football OR soccer OR (indoor AND soccer) OR futsal OR rugby OR (rugby AND league) OR (rugby AND union) OR (gaelic AND football) OR 'australian rules footbal' OR (('australian'/exp OR australian) AND rules AND footbal) OR afl OR 'american football'/exp OR 'american football' OR (('american'/exp OR american) AND ('football'/exp OR football)) OR 'gridiron football' OR (gridiron AND ('football'/exp OR football)) OR 'touch football' OR (('touch'/exp OR touch) AND ('football'/exp OR football))) AND [2019-2019]/py",
             "#1 AND #2 AND [english]/lim AND 2019:py",
             "Articles: 1,756",
             ""),
  Cinahl = c("exercise science OR sports science OR physiology OR biomechanics OR nutrition OR training OR testing OR sports medicine OR performance analysis OR performance OR sport psychology OR coaching",
              "football OR soccer OR indoor soccer OR futsal OR rugby league OR rugby union OR gaelic football OR australian rules football OR AFL OR american football OR gridiron football OR touch football",
              "Published Date: 20190101-20191231; English Abstract Available; Peer Reviewed",
              "Articles: 735",
              "https://gateway.library.qut.edu.au/login?url=https://search.ebscohost.com/login.aspx?direct=true&db=c8h&bquery=(+exercise+science+OR+sports+science+OR+physiology+OR+biomechanics+OR+nutrition+OR+training+OR+testing+OR+sports+medicine+OR+performance+analysis+OR+performance+OR+sport+psychology+OR+coaching+)+AND+(+football+OR+soccer+OR+indoor+soccer+OR+futsal+OR+rugby+league+OR+rugby+union+OR+gaelic+football+OR+australian+rules+football+OR+AFL+OR+american+football+OR+gridiron+football+OR+touch+football+)&cli0=DT1&clv0=201901-201912&authtype=sso&custid=qut&type=1&searchMode=Standard&site=ehost-live&scope=site")

)

search_table %>% 
  gt() %>% 
  cols_width(
    vars(Sportdiscus, Cinahl) ~ px(240),
    vars(Embase) ~ px(300)
    )
```

@@

```{r prisma, fig.cap = "Write the figure caption here"}
  # | Imported                            | 3,863                             |
  # | After duplicates removed            | 1,954                             |
  # | After title and abstract screen     | 1,373                             |
  # | Random sample for full-text screen  | 199 (needed for 10% inclusion)    |
  # | Full-text included                  | 137                               |
  # | Full-text excluded                  | Full-text papers excluded (n=62)  |

prisma(found = 3863,
       found_other = F,
       no_dupes = 1954, 
       screened = 1373, # (1954 - 1373) 
       screen_exclusions = 581, 
       full_text = 199,
       full_text_exclusions = 62, 
       qualitative = 137, 
       quantitative = 0,
       width = 800, height = 800,
       labels = list(
full_text_exclusions = "Full text articles excluded (n = 62),
with reasons:
Commentary/letter (n = 4),
Conference abstract (n = 21),
Full-text not available (n = 9),
Infographic (n = 2),
Not in English (n = 17),
Qualitative study (n = 9)
"))

@@

The search returned a total of 3,863 articles (Figure 1). Of the 199
articles screened, 137 were deemed eligible, representing \~10% of total
articles published on football related studies in 2019 (Figure 1). The
proportion of articles that reported missing data was 5.9% \[95% confidence
interval; X% to X%\] or 8/136. A breakdown of the extracted information
is provided in Table 2.

>>>>

---
title: "Supplement 2"
output: 
  bookdown::html_document2:
    keep_md: true
  bookdown::pdf_document2:
    toc: false
bibliography: "supp2.bib"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      fig.align = "center")
```

```{r libraries, message = FALSE}
library(tidyverse)
library(kableExtra)
library(knitr)
library(conflicted)
library(gt)
library(PRISMAstatement)
library(DiagrammeRsvg)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")
```

@@

Football related articles published in 2019 were studied. Three major
sports medicine databases were searched on May 20, 2020, using key terms and limits. 
The databases were: SPORTDiscus, Embase and Cinahl. A
list of the search terms and complete search statements are provided in
Table \@ref(tab:search-table-print) below.

```{r search-table}
table_terms <- tibble(
  SPORTDiscus = c("exercise science OR sports science OR physiology OR biomechanics OR nutrition OR training OR testing OR sports medicine OR performance analysis OR performance OR sport psychology OR coaching",
    "football OR soccer OR indoor soccer OR futsal OR rugby league OR rugby union OR gaelic football OR australian rules football OR AFL OR american football OR gridiron football OR touch football"),
  Embase = c("(exercise AND science OR (sports AND science) OR physiology OR biomechanics OR nutrition OR training OR testing OR (sports AND medicine) OR 'performance analysis' OR (('performance'/exp OR performance) AND ('analysis'/exp OR analysis)) OR 'performance'/exp OR performance OR 'sport psychology'/exp OR 'sport psychology' OR (('sport'/exp OR sport) AND ('psychology'/exp OR psychology)) OR 'coaching'/exp OR coaching) AND [2019-2019]/py",
              "(football OR soccer OR (indoor AND soccer) OR futsal OR rugby OR (rugby AND league) OR (rugby AND union) OR (gaelic AND football) OR 'australian rules footbal' OR (('australian'/exp OR australian) AND rules AND footbal) OR afl OR 'american football'/exp OR 'american football' OR (('american'/exp OR american) AND ('football'/exp OR football)) OR 'gridiron football' OR (gridiron AND ('football'/exp OR football)) OR 'touch football' OR (('touch'/exp OR touch) AND ('football'/exp OR football))) AND [2019-2019]/py"),
  Cinahl = c("exercise science OR sports science OR physiology OR biomechanics OR nutrition OR training OR testing OR sports medicine OR performance analysis OR performance OR sport psychology OR coaching",
              "football OR soccer OR indoor soccer OR futsal OR rugby league OR rugby union OR gaelic football OR australian rules football OR AFL OR american football OR gridiron football OR touch football")

)
```

```{r notes-to-add-for-index, echo = FALSE, eval = FALSE}
# from sport discuss
# "Published Date: 20190101-20191231; English Abstract Available; Peer Reviewed"
# "Articles: 1,372"

# from Embase
# "#1 AND #2 AND [english]/lim AND 2019:py"
# "Articles: 1,756"

# from Cinahl
# "Published Date: 20190101-20191231; English Abstract Available; Peer Reviewed"
# "Articles: 735"
```

```{r search-table-print}
table_terms %>% 
  kable(caption = "Key search terms and complete search statements and limits for the databases, SPORTDiscuss, Embase, and Cinahl") %>% 
  kable_styling("striped",
                full_width = TRUE) 
```

@@

```{r prisma, fig.cap = "Flowchart of the article search and inclusion for the systematic search. The full-text of 137 articles was reviewed.", warning = FALSE, fig.height = 10, fig.width = 8}
prisma(found = 3863,
       found_other = F,
       no_dupes = 1954, 
       screened = 1373, # (1954 - 1373) 
       screen_exclusions = 581, 
       full_text = 199,
       full_text_exclusions = 62, 
       qualitative = 137, 
       quantitative = 0,
       width = 800, 
       height = 800,
       font_size = 16,
       labels = list(
full_text_exclusions = "Full-text articles excluded (n = 62),
with reasons:
Commentary/letter (n = 4),
Conference abstract (n = 21),
Full-text not available (n = 9),
Infographic (n = 2),
Not in English (n = 17),
Qualitative study (n = 9)
"))

@@

The search returned a total of 3,863 articles (Figure \@ref(fig:prisma)). Of the 199
articles screened, 137 were deemed eligible, representing \~10% of total
articles published on football related studies in 2019 (Figure 1). The
proportion of articles that reported missing data was 5.9% \[95% confidence
interval; X% to X%\] or 8/136. A breakdown of the extracted information
is provided in Table 2.

```{r read-gs-data}
